Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-27 edubots_surveys.Rnw
Update edubots_surveys.Rnw

%%% Begin ...
\begin{document}
%\SweaveOpts{concordance=TRUE}

@@

>>>>

%%% Begin ...
\begin{document}
\SweaveOpts{concordance=TRUE}
%\SweaveOpts{concordance=TRUE}

@@

Answer to these questions are plotted in Figure \ref{figure:chatbots_types} grouped by gender, sector and experience. As it was a multiple choice question, the counts are over the total number of people that answered. One of the most interesting questions that can arise from the plots, and the should require further study, is: Are our professors really aware of the possibilities of chatbots in the classroom? The reason to ask ourselves this question is due to the fact of the small number of responses for other uses in comparison with the other approaches proposed. Another way to loook about it is that, unless you provide the specific instructions on how to use a tool, the teaching staff is already too busy or burn out to think about innovation.

Regarding Gender grouping, both gender agree in their uses, so it seems not relevant at all. When looking at the plot containing the sector differentiation it is interesting ot observe how university professors prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational/High School teachers. This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform. Furthermore, the high student/professor ratios that university professors have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs. This could ameliorate the number of misunderstandings and email overload that so many students might generate.

The results, when grouping by experience, confirm the previous observation that experienced professors are not afraid of changes and are willing to accept new technological challenges, at least, in the same way that younger professors are. From this concrete plot it is interesting as well the fact that very few young/inexperience professors are willing to use chatbots for other uses. This reinforces the hypothesis thrown at the beginning of this section and, as these professors have less experience, they also have less field of view to think about ways of using chatbots.
